---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: 'Helvetica Neue', sans-serif;
  background: linear-gradient(to bottom right, #feda75, #fa7e1e, #d62976, #962fbf, #4f5bd5);
  color: white;
  padding: 30px;
}

h2 {
  color: white;
  text-shadow: 1px 1px 2px #00000070;
  border-bottom: 2px solid white;
  padding-bottom: 5px;
  margin-top: 40px;
}

p {
  font-size: 16px;
  line-height: 1.6;
}


```

## What Kind of Ads Are We Seeing on Instagram and What Patterns Can We Concur From Them?

This dynamic report will present insights based on observational data collected from Instagram scrolling sessions that have been done in 5 mintute intervals. The user will record the number of ads they see, the most common ad category, and what time of day they were scrolling.



```{r}
library(tidyverse)

# Read and clean data

latest_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQoCQHaq2daCo0bYJ6NV3gSLRTd6suzq3LDb-eBpZJ7eSfG9Mnrrqvh7TMlpzm8OXXml-5sbFIMun1S/pub?output=csv") %>%
  rename(
    ad_count = `How many ads did you see during this scrolling session?`,
    ad_category = `What was the most common ad category shown?`,
    time_of_day = `What time of day were you scrolling?`
  ) %>%
  mutate(ad_count = as.numeric(ad_count))

# Summary statistics

mean_ads <- mean(latest_data$ad_count, na.rm = TRUE)
max_ads <- max(latest_data$ad_count, na.rm = TRUE)




```

On average, we saw `r round(mean_ads, 1)` ads during a scrolling session.  
The highest number of ads seen in a single session was `r max_ads`.

```{r}
# Bar Chart 1 - Frequency of Ad Category

ggplot(latest_data, aes(x = ad_category)) +
  geom_bar(fill = "skyblue") +
  labs(title = "Most Common Ad Categories", x = "Ad Category", y = "Count") +
  theme_minimal()

# Bar Chart 2 - Average Ads by Time of Day

latest_data %>%
  group_by(time_of_day) %>%
  summarise(avg_ads = mean(ad_count, na.rm = TRUE)) %>%
  ggplot(aes(x = time_of_day, y = avg_ads)) +
  geom_col(fill = "coral") +
  labs(title = "Average Ads Seen by Time of Day", x = "Time of Day", y = "Average Ads") +
  theme_minimal()


```


The most frequently shown ad category across all sessions was `r latest_data %>% count(ad_category) %>% arrange(desc(n)) %>% slice(1) %>% pull(ad_category)`, which appeared `r latest_data %>% count(ad_category) %>% arrange(desc(n)) %>% slice(1) %>% pull(n)` times in the dataset.


### Summary

This report explores observational data collected on Instagram advertisements during five-minute scrolling sessions. Users were asked to report how many ads they saw, the most common ad category, and the time of day they were scrolling. The two visualisations below summarize the most frequent ad categories observed and the average number of ads seen during different times of the day.

The first chart shows that **Tech/Gadgets** ads were the most commonly reported category, making up nearly half of the responses. This suggests a clear trend in Instagram’s ad targeting, possibly aligned with users' tailored interests or trending tech content. **Fitness/Health** and **Food/Restaurants** also appeared frequently, while **Entertainment** ads were reported the least.

The right chart presents the **average number of ads seen** based on the time of day. **Evening and night sessions** had the **highest average ad exposure**, hovering around 19 ads on average. **Afternoon** scrolling sessions had nearly the same amount, while **morning** sessions had the lowest, with around 17 ads on average. This pattern may be due to ad volume scheduling by Instagram or user engagement patterns throughout the day.

These results suggest both **what** Instagram is promoting most frequently, and **when** users are most shown advertisements. This could better inform future studies into digital marketing strategy, attention research, or even user well-being concerning screen time and targeted content.



**Inspired by the colorful and chaotic nature of Instagram ads.**

